\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150. Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases. Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively. In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Table~\ref{table:Heleshaw}). Such calculated \citep[\ie theoretical based on simplified mathematical formulation due to][]{mclean_1981} ranges clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) does not take into account spatial variability of heterogeneity.

\red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.

>>>>

In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150. Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases. Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively. In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}). Such calculated \citep[\ie theoretical based on simplified mathematical formulation due to][]{mclean_1981} ranges clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) does not take into account spatial variability of heterogeneity.
